---
title: "MDS example"
author: "Michael A. Kriegsman"
date: "July 09, 2017"
output: html_document
#output: pdf_document
#keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DistatisR)
library(ExPosition)
library(DiDiSTATIS)
```

## Example: DiMDS

#The data, S
For this example, I adapt the data from the chapter on DiSTATIS.
Although these data are an array of distance matrices, DiSTATIS collapses 
the tables into a single representative table, called the compromise.
This compromise is a 36 by 36 (psd) matrix of the perceived similarity 
between 36 pieces of classical music. 
Here, I denote the compromise S, where S is the input to DiMDS. 
(Note that in DiSTATIS, the compromise is called Splus)

```{r TheData}
## Archived Notes
## I ran DiDiSTATIS_Composers_free_36.R (despite the name, this is a standard DiSTATIS) on 5.16.17 and saved out compromise as CompromiseForDiMDS
## S <- RvDiSTATIS_Composers.res$res4GPCA$Splus
## save("S", file = "CompromiseForDiMDS.rda")


#read in the data, S, the compromise from DiSTATIS (from Part II of the dissertation).
load('C:/Users/Michael A. Kriegsman/Google Drive/Dissertation/DiDiSTATIS/DiDiSTATIS/vignettes/DiMDS/CompromiseForDiMDS.rda')
#round(S, 3)
```

#The design, B
The pieces of classical music (stimuli, rows)
are organized into a 2-factor completely between design. That is, 
each piece was composed by 1 of 3 composers, and played by 1 of 4 
pianists. For the dissertation proposal, I will only investigate
the effect of composer. 

```{r DESIGN$rows}
#create the design. B, the design matrix for the A=36 musical pieces nested in the B=3 composers.
source('C:/Users/Michael A. Kriegsman/Google Drive/Dissertation/DiDiSTATIS/DiDiSTATIS/vignettes/Initialize_Dowling_NaturalStimuli_Example.R')
```

#Let's go!

```{r DiMDS}
res_MDS <- MDS(D = S, data_are = 'CP', DESIGN = DESIGN, main = 'FreeSort36 Composers')
#Feed DiMDS the goods
res_DiMDS <- DiMDS(D = S, data_are = 'CP', DESIGN_rows = B, main = 'FreeSort36 Composers')
```

Consider the effect size(s):

$r^2_{Total \cdot B}$
```{r}
#The portion of the total barycentric space explained by the barycenters (Composers)
round(res_DiMDS$r2$total.b,3)
```

$r^2_{TotalTotal \cdot B}$
```{r}
#The portion of the original data explained by the barycenters (Composers)
round(res_DiMDS$r2$totaltotal.b,3)
```

There is a large discrepency between the size of the barycentric space and the size of the original data.   
This shows that the hypothesized between-group effect is small (and/or the data are highly variable).

Given the small effect, let's inspect, respectively, 
Fb: the group barycenters in the barycentric factor scores,
F:  the original data projected intot he barycentric factor space
...

